\chapter{Requirements Traceability}

The traceability matrix provided below aims to establish a clear connection between the requirements outlined in the Requirements Analysis and Specification Document (RASD) and the components of the Student\&Companies system responsible for addressing them. 

The referenced components are discussed in greater detail in Section 2.2, Component View, of this Design Document, where their roles and responsibilities within the system are thoroughly explained.


\begin{longtable}{p{0.10\textwidth}p{0.35\textwidth}p{0.35\textwidth}}
    \textbf{ReqID} & \textbf{Requirement Description} & \textbf{Components Involved} \\
    \vspace{0.5em}\\
    \hline
    \vspace{0.5em}\\
    \endfirsthead
    \textbf{ReqID} & \textbf{Requirement Description} & \textbf{Components Involved} \\
    \vspace{0.5em}\\
    \hline
    \vspace{0.5em}\\
    \endhead

    R1.1 &
    The system allows students to create their profile. &
    Gateway Microservice (Dispatcher), User Management Microservice (Student Manager). \\
    \vspace{0.5em}\\
    R1.2 &
    The system allows students to upload their CV. &
    Gateway Microservice (Dispatcher), User Management Microservice (Student Manager), Recommendation System Microservice (Recommendation System Manager). \\
    \vspace{0.5em}\\
    R1.3 &
    The system provides suggestions to students on how to submit their CV. &
    Gateway Microservice (Dispatcher), User Management Microservice (Student Manager). \\
    \vspace{0.5em}\\
    R1.4 &
    The system allows students to browse internships. &
    Gateway Microservice (Dispatcher), Selection Process Microservice (Selection Process Manager, Selection Process Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R2.1 &
    The system allows companies to create their profile. &
    Gateway Microservice (Dispatcher), User Management Microservice (Company Manager). \\
    \vspace{0.5em}\\
    R2.2 &
    The system allows companies to upload their internships. &
    Gateway Microservice (Dispatcher), User Management Microservice (Company Manager), Recommendation System Microservice (Recommendation System Manager). \\
    \vspace{0.5em}\\
    R2.3 &
    The system provides suggestions to companies on how to submit their internship descriptions. &
    Gateway Microservice (Dispatcher), User Management Microservice (Company Manager) \\
    \vspace{0.5em}\\
    R3.1 &
    The system notifies students about suitable internships. &
    Recommendation System Microservice (Recommendation System Manager, Recommendation System Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R3.2 &
    The system notifies companies about suitable student CVs. &
    Recommendation System Microservice (Recommendation System Manager, Recommendation System Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R3.3 &
    The system recommends based on keyword searching. &
    Recommendation System Microservice (Recommendation System Manager, Recommendation System Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R3.4 &
    The system recommends based on the characteristics of students and internships. &
    Recommendation System Microservice (Recommendation System Manager, Recommendation System Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R3.5 &
    The system recommends based on statistical analysis. &
    Statistical Analysis Tool, Recommendation System Microservice (Recommendation System Manager, Recommendation System Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R3.6 &
    The system collects information regarding the selection process. &
    Selection Process Microservice (Selection Process Manager), Gateway Microservice (Dispatcher) \\
    \vspace{0.5em}\\
    R3.7 &
    The system collects information regarding the internship. &
    Internship Microservice (Internship Manager, Internship Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer), Gateway Microservice (Dispatcher) \\
    \vspace{0.5em}\\
    R3.8 &
    The system asks students and companies to provide feedback and suggestions. &
    Feedback\&Complaint Microservice (Feedback\&Complaint Manager), Gateway Microservice (Dispatcher) \\
    \vspace{0.5em}\\
    R4.1 &
    The system allows students to apply for an internship. &
    Gateway Microservice (Dispatcher), Selection Process Microservice (Selection Process Manager, Selection Process Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R4.2 &
    The system allows companies to accept student applications. &
    Gateway Microservice (Dispatcher), Selection Process Microservice (Selection Process Manager, Selection Process Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R4.3 &
    The system allows students to sign the contract for the internship. &
    Selection Process Microservice (Selection Process Manager), Gateway Microservice (Dispatcher), Feedback\&Complaint Microservice (Feedback\&Complaint Manager) \\
    \vspace{0.5em}\\
    R4.4 &
    The system allows companies to sign the contract for the internship. &
    Selection Process Microservice (Selection Process Manager), Gateway Microservice (Dispatcher), Feedback\&Complaint Microservice (Feedback\&Complaint Manager) \\
    \vspace{0.5em}\\
    R4.5 &
    The system supports the selection process by helping manage interviews and also finalise the selections. &
    Selection Process Microservice (Selection Process Manager), Gateway Microservice (Dispatcher), Feedback\&Complaint Microservice (Feedback\&Complaint Manager) \\
    \vspace{0.5em}\\
    R5.1 &
    The system provides spaces for the official announcements. &
    Internship Microservice (Internship Manager, Internship Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R5.2 &
    The system provides spaces where interested parties can complain, communicate problems, and provide information about the current status of the ongoing internship. &
    Communication Platform Microservice (Communication Platform Manager, Communication Platform Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer), Gateway Microservice (Dispatcher) \\
    \vspace{0.5em}\\
    R6.1 &
    The system allows universities to create their profile. &
    Gateway Microservice (Dispatcher), User Management Microservice (University Manager). \\
    \vspace{0.5em}\\
    R6.2 &
    The system allows universities to monitor the situation of internships and handle complaints. &
    Feedback\&Complaint Microservice (Feedback\&Complaint Manager, Feedback\&Complaint Event Publisher), Notification Microservice (Notification Manager, Notification Event Consumer) \\
    \vspace{0.5em}\\
    R6.3 &
    The system allows universities to interrupt an internship. &
    Gateway Microservice (Dispatcher), Internship Microservice (Internship Manager, Internship Event Publisher), User Management Microservice (Student Manager, Company Manager), Notification Microservice (Notification Manager, Notification Event Consumer) \\

\end{longtable}