\chapter{User Interface Design}
This chapter displays a more in depth analysis of the ”3.1.1" section called "User Interface” of the
 Requirements Analysis and
 Specification Document (RASD) related to the S\&C project. 
 Within the scope of detail permitted in a design document, 
 it is possible to explore the various interactions the platform provides to external users,
  whether they are students or companies' employees.
 The screenshots displayed in this section serve as mockups of the user interfaces provided by the system, 
 therefore they have to be interpreted as general guidelines for the designers and developers to
 grasp the application overall look at the end of the implementation process.



\section{NavBar}
The navbar is the cardinal navigational component of the S\&C platform, 
designed to provide quick and intuitive access to the platform's core features. 
It features a minimalist, user-friendly design with the following icons:  

\begin{itemize}
    \item Messages: Provides access to the messaging interface, 
    allowing real-time communication between students and companies.  
    \item Inbox: Displays notifications, updates, 
    and invitations from companies or students in a streamlined format.  
    \item Search: Redirects to the Internship Browsing Page,
    enabling users to find internships, through either a keyword search or recommended hot topics.
    \item Profile: Takes users to their profile page, 
    where they can view and edit their information, CV, or internships offers (depending on the user).  
\end{itemize}



The navbar ensures a seamless user experience, remaining accessible across all pages of the platform.

\section{Login Page}
\section{Student Profile}
\section{Company Profile}
\section{Notification Inbox}
\section{Internship Browsing Page}
\section{Internship Information Details}
\section{Chat}
\section{Feedback/Complaint}
\section{Internship Creation Form}
\section{Preliminary Questionnaire}




