\chapter{Introductionn}

% //////////////////////////////
% ------------------------------
\section{Purpose}
% ------------------------------
% //////////////////////////////

The \textit{Students\&Companies (S\&C)} platform bridges the gap between university students seeking internships and companies offering them. It simplifies the process of matching students with internship opportunities based on their skills, experiences, and preferences, as well as companies' requirements and offered benefits.

The software involves three main actors: \textbf{students}, \textbf{companies}, and \textbf{universities}.

\begin{itemize}
    \item \textbf{Students} use the platform to search and apply for internships, submit their CVs, and receive recommendations tailored to their profiles.
    \item \textbf{Companies} advertise internships, specify requirements, and manage the selection process for suitable candidates.
    \item \textbf{Universities} monitor the execution of internships and handle complaints or issues that may arise.
\end{itemize}

S\&C features a \textbf{recommendation system} that matches students and internships using mechanisms ranging from keyword-based searches to advanced statistical analyses. The platform also facilitates communication, supports the selection process, and tracks internship progress to ensure transparency for all involved parties.

The main objectives of the system can be summarized as follows:

\begin{itemize}
    \item \textbf{G1)} The system allows students to proactively look for internships.
    \item \textbf{G2)} The system allows companies to advertise the internships that they offer.
    \item \textbf{G3)} The system recommends students suitable internships based on their CVs and recommends companies student CVs corresponding to their needs.
    \item \textbf{G4)} The system enables students and companies to initiate and manage the selection process.
    \item \textbf{G5)} The system allows communication between the two parties throughout the ongoing internship process.
    \item \textbf{G6)} The system allows universities to monitor internships and handle complaints.
\end{itemize}

% //////////////////////////////
% ------------------------------
\section{Scope}
% ------------------------------
% //////////////////////////////

The \textit{Students\&Companies (S\&C)} platform is designed to address the challenge of connecting university students seeking internship opportunities with companies offering them. By streamlining the entire internship lifecycle, S\&C simplifies the processes of advertisement, recommendation, selection, and management of internships, creating value for students, companies, and universities alike.

The platform allows students to actively search for internships by browsing opportunities advertised by companies. Students can upload their CVs, highlighting their skills, experiences, and attitudes, and receive tailored recommendations based on the relevance of their profiles to available internships. These recommendations are generated using mechanisms that range from basic keyword searches to advanced statistical analyses. This ensures that students are made aware of internships that align with their skills and preferences while helping companies identify candidates who meet their requirements. Beyond recommendations, students can also take the initiative to directly apply for internships of interest.

For companies, S\&C serves as a centralized platform to advertise internships and specify essential details such as the application domain, required tasks, adopted technologies, and offered benefits, including tangible incentives like stipends or intangible elements such as mentorship and training. Through its recommendation system, the platform automatically identifies and suggests student CVs that best fit the company’s specified needs. Once a mutual interest is established, the platform facilitates the subsequent selection process by supporting interview scheduling, managing communication between companies and students, and even offering tools like structured questionnaires to streamline evaluations.

Universities play a monitoring role within the system. Given their responsibility to oversee internships and ensure their educational value, universities can track ongoing internships through the platform. They are empowered to handle complaints or intervene in cases where conflicts arise, including managing serious issues that might necessitate the interruption of an internship. This oversight mechanism helps maintain a standard of quality and accountability across all internships facilitated by the platform.

The platform also supports communication and transparency throughout the internship process. Once students and companies establish contact, S\&C provides mechanisms to manage interviews and selections, ensuring that both parties remain engaged and informed. During the internship, the platform allows ongoing communication between students and companies, helping address concerns, report progress, and resolve issues as they arise. Additionally, the system collects feedback from all parties, which serves as valuable input for refining recommendations and improving the overall efficiency of the platform.

A critical aspect of S\&C is its focus on tracking and monitoring the outcomes of internships. Companies and students can provide updates and feedback regarding the progress of ongoing internships, ensuring transparency and accountability for all actors involved. This information not only helps universities oversee the process but also contributes to the continuous improvement of the platform’s recommendation and matching mechanisms.

Overall, the \textit{Students\&Companies} platform integrates proactive internship searching, intelligent recommendation, seamless communication, and effective monitoring to create an ecosystem that benefits students, companies, and universities. By simplifying each phase of the internship lifecycle, S\&C promotes meaningful matches between students and opportunities, fostering better experiences and outcomes for all stakeholders involved.

% //////////////////////////////
% ------------------------------
\subsection{World, Machine and Shared Phenomena}
% ------------------------------
% //////////////////////////////

This section summarizes the previous description into lists of phenomena (events) that occur in the
world of interest for the system to be developed. Phenomena have to be interpreted simply as events
occurring in the whole domain that is being analyzed in the document, so they have been stripped of
any constraint (that will be better specified in the requirements section).

Phenomena can be divided into:
\begin{itemize}
    \item \textbf{World phenomena:} events happening outside the system and on which the system has no control.
    \item \textbf{Machine phenomena:} events happening internally in the system, independent from the outside world.
    \item \textbf{Shared phenomena:} events that have an influence on both the system and the world surrounding it. Usually they are further split into two classes:
    \begin{itemize}
        \item \textbf{World controlled shared phenomena:} events initiated by entities of the world that are impactful for the system.
        \item \textbf{Machine controlled shared phenomena:} events triggered or initiated by the system with a relevant impact in the domain in which the system works.
    \end{itemize}
\end{itemize}

% //////////////////////////////
% ------------------------------
\subsubsection{World Phenomena}
% ------------------------------
% //////////////////////////////

\begin{itemize}
    \item \textbf{WP1)} \textbf{Student} wants to begin an internship.
    \item \textbf{WP2)} \textbf{Student} writes their CV.
    \item \textbf{WP3)} \textbf{Company} engages in the development and execution of projects.
    \item \textbf{WP4)} \textbf{Company} aims to present and showcase their projects.
    \item \textbf{WP5)} \textbf{Company} needs staff.
    \item \textbf{WP6)} \textbf{University} wants to monitor the situation of its students.
\end{itemize}

% //////////////////////////////
% ------------------------------
\subsubsection{Machine Phenomena}
% ------------------------------
% //////////////////////////////

\begin{itemize}
    \item \textbf{MP1)} \textbf{The system} collects data of students' CV, analyzes them and identifies a company that may be suitable for the student.
    \item \textbf{MP2)} \textbf{The system} collects data of internships, analyzes them and identifies a student that may be suitable for the company.
    \item \textbf{MP3)} \textbf{The system} collects data regarding internships and feedback from both parties to carry out statistical analyzes in order to refine the recommendation process.
    \item \textbf{MP4)} \textbf{The system} is able to provide suggestions both to companies and to students regarding how to make their submissions.
    \item \textbf{MP5)} \textbf{The system} supports the selection process by helping manage (set up, conduct, etc.) interviews and also allows to finalize the selections.
\end{itemize}

% //////////////////////////////
% ------------------------------
\subsubsection{World Controlled Shared Phenomena}
% ------------------------------
% //////////////////////////////

\begin{itemize}
    \item \textbf{WSP1)} \textbf{Student} creates their personal profile on the platform uploading their personal information.
    \item \textbf{WSP2)} \textbf{Student} uploads his/her CV.
    \item \textbf{WSP3)} \textbf{Student} applies for an available internship.
    \item \textbf{WSP4)} \textbf{Company} creates its personal profile.
    \item \textbf{WSP5)} \textbf{Company} uploads on the platform an available project comprehensive of all the details such as (application domain, tasks to be performed, relevant adopted technologies-if any, benefits, mentorship).
    \item \textbf{WSP6)} \textbf{University} creates its own profile on the platform.
    \item \textbf{WSP7)} \textbf{Company} accepts the \textbf{Student} for the interview.
    \item \textbf{WSP8)} \textbf{Student} fills the preliminary questionnaire.
    \item \textbf{WSP9)} \textbf{Company} reports preliminary questionnaire progress.
    \item \textbf{WSP10)} \textbf{Company} starts selection process.
    \item \textbf{WSP11)} \textbf{Company} finalizes the selection.
    \item \textbf{WSP12)} \textbf{Student} communicates in the provided space.
    \item \textbf{WSP13)} \textbf{Company} communicates in the provided space.
    \item \textbf{WSP14)} \textbf{University} reads complaints.
    \item \textbf{WSP15)} \textbf{University} requires the interruption of the internship.
\end{itemize}

% //////////////////////////////
% ------------------------------
\subsubsection{Machine Controlled Shared Phenomena}
% ------------------------------
% //////////////////////////////

\begin{itemize}
    \item \textbf{MSP1)} \textbf{The system} notifies the \textbf{Student} if it identifies an internship that matches his skills.
    \item \textbf{MSP2)} \textbf{The system} notifies the \textbf{Company} if it identifies a \textbf{Student} who matches the requirements for the internship.
    \item \textbf{MSP3)} \textbf{The system} collects feedback from \textbf{Students} and \textbf{Companies} during the recommendation process.
    \item \textbf{MSP4)} \textbf{The system} notifies the \textbf{University} of a complaint.
\end{itemize}

\newpage
% //////////////////////////////
% ------------------------------
\section{Definitions, Acronyms, Abbreviations}
% ------------------------------
% //////////////////////////////

% //////////////////////////////
% ------------------------------
\subsection{Definitions}
% ------------------------------
% //////////////////////////////

A brief list of the most meaningful and relevant terms and synonyms used in this document is reported
here, in order to make reading process smoother and clearer:

\begin{longtable}{|p{0.50\textwidth}|p{0.50\textwidth}|}
    \hline
    \textbf{Term} & \textbf{Description} \\
    \hline
    \endfirsthead
    \hline
    \textbf{Term} & \textbf{Description} \\
    \hline
    \endhead
    \hline
    \endfoot
    
    Internship, Placement, Work-Experience & A temporary work opportunity offered by a company, designed for students to gain practical experience in a professional environment while applying their academic knowledge. \\
    \hline
    CV, Resume & A document created by a student containing their personal information, skills, educational background, and work experience, used to apply for internships or jobs. \\
    \hline
    Recommendation System, Suggestion System & A feature of the platform that identifies and matches suitable internships for students or suitable candidates for companies based on their profiles, preferences, and requirements. \\
    \hline
    Student Profile & A digital representation of a student within the system, containing personal details, uploaded CVs, skills. \\
    \hline
    Company Profile & A digital representation of a company within the system, containing details about the company, uploaded projects or internships. \\
    \hline
    Recommendation Process & The sequence of steps executed by the system to align the skills and preferences of students with the requirements of available internships offered by companies. \\
    \hline
    Feedback, Suggestions & Information collected from students and companies after the internship or during the process to refine the matching system and improve user satisfaction. \\
    \hline
    Communication Space, Chat Feature, Messaging System & A feature in the platform that allows students, companies, and universities to interact and share important updates or resolve concerns. \\
    \hline
    Selection Process & A phase in which companies evaluate student applications, conduct interviews, and finalize the selection of candidates for internships. \\
    \hline
    Interview Setup, Interview Management & The process supported by the system to schedule, conduct, and manage interviews between companies and students. \\
    \hline
    Monitoring by University & The process where the university oversees the activities and outcomes of student internships and intervenes if necessary. \\
    \hline
    Complaint Resolution & The process of identifying and addressing issues raised by students or companies during or after the internship period. \\
    \hline
    Submission Deadline, Application Deadline & The last date for students to submit applications for an internship or for companies to post available projects on the platform. \\
    \hline
    Notification System, Alert System & A functionality in the platform that keeps users informed about new opportunities, deadlines, or important events. \\
    \hline
    Platform, System, Application & All synonyms for the software platform being developed to manage the interactions and processes related to internships. \\
    \hline
    Statistical Analysis & The process by which the system evaluates collected feedback and interactions to improve its recommendation algorithms and user experience. \\
    \hline
    
\end{longtable}

% //////////////////////////////
% ------------------------------
\subsection{Acronyms}
% ------------------------------
% //////////////////////////////

A list of acronyms used throughout the document for simplicity and readability:

\begin{enumerate}
    \item RASD - Requirements Analysis and Specification Document
    \item S\&C - Students\&Companies
\end{enumerate}

\newpage
% //////////////////////////////
% ------------------------------
\section{Reference Documents}
% ------------------------------
% //////////////////////////////

Here’s a list of reference documents that have been used in order to shape the Requirements Analysis and Specification Document of the \textit{Students\&Companies} system. In the following, all external sources of information that have contributed to the design of this document are mentioned.

\begin{enumerate}
    \item Stakeholders’ specification provided by the R\&DD assignment for the Software Engineering II course at Politecnico Di Milano for the year 2024/2025.
    \item ``29148-2018, ISO/IEC/IEEE International Standard, Systems and software engineering, Life cycle processes, Requirements engineering'', by IEEE, 2018. \\
    Link: \url{https://ieeexplore.ieee.org/document/8559686}
    \item UML specifications, version 2.5.1. \\
    Link: \url{https://www.omg.org/spec/UML/2.5.1/About-UML}
    \item Alloy documentation, version 6.1.0.8. \\
    Link: \url{https://alloy.readthedocs.io/en/latest/}
\end{enumerate}

\newpage
% //////////////////////////////
% ------------------------------
\section{Document Structure}
% ------------------------------
% //////////////////////////////

This Requirements and Analysis Specification Document is composed of four major sections.

The \textbf{Introduction} serves to familiarize the reader with the domain relevant to the system being developed. It primarily uses natural language to describe the fundamental actors and elements involved in the interactions between the system and its external environment. \\
The \textbf{Purpose} section outlines the primary goals of the application. \\
The \textbf{Scope} section reinterprets the original stakeholders’ requirements into a new, high-level description of the domain. Its aim is to ensure clarity and eliminate ambiguity. This section identifies the key actors within the system's environment, explains their roles, and briefly outlines the interactions between these actors and the system. This high-level overview provides context for the remainder of the document and supports the justification of design decisions presented later in the RASD. Following this, the description transitions into defining the system, the external world, and machine-related phenomena. \\
The \textbf{Definitions} subsection clarifies the terminology and vocabulary used throughout the document, minimizing potential ambiguity. It includes a table listing synonyms for terms employed in the RASD to ensure consistency and understanding.

The second major section of this document is the \textbf{Overall Description}, which serves multiple purposes through its subsections. \\
The first subsection focuses on \textbf{Scenarios}, aiming to validate the stakeholders’ needs by presenting concrete examples and instances of interactions with the system under development. \\
The \textbf{Domain Class Diagram} and \textbf{State Charts} subsections utilize UML diagrams to provide a graphical representation of the domain of interest, aligning with the details introduced earlier in the document. \\
The \textbf{Product Functions} subsection systematically lists the system's functional requirements. This analysis builds on the previous sections, leveraging the insights gained from observing and describing the domain to identify the necessary system requirements. \\
Lastly, the \textbf{Assumptions, Dependencies, and Constraints} subsection enumerates domain elements and events that lie outside the system’s control or involve dependencies on external factors.

The third main section of this RASD, \textbf{Specific Requirements}, focuses on transforming the functional requirements outlined in the Product Functions section into structured and graphical representations. \\
The \textbf{External Interface Requirements} subsection addresses the interfaces and interaction modes between the system and external users or software products. \\
The \textbf{Functional Requirements} subsection provides a structured view of the functional requirements using tools like use cases, use case diagrams, and sequence diagrams. It also includes a mapping between these graphical elements and their associated requirements. \\
The \textbf{Design Constraints} subsection outlines the constraints the system must adhere to during development. The \textbf{Software System Attributes} subsection specifies the qualities the software must possess, such as reliability and availability, along with approaches to achieving them. \\
The final section, \textbf{Alloy}, presents an analysis of the system using Alloy, a tool designed to evaluate system design correctness.