\chapter{Per fare prove}

Ciao ragazzi come va?

Guardate questo link importantissimo: \citep{provaBibliografia}


Questo lo ho aggiunto dopo.

Questo aggiunto dopo da VS code direttamente.


modifica in chimata


    \begin{table}[h!]
        \centering
        \begin{tabularx}{\textwidth}{XXXX} % La tabella ora si espande alla larghezza della pagina
        \toprule
        \textbf{Requirement} & \textbf{Goal} & \textbf{UseCase} & \textbf{SequenceDiagram} \\
        \midrule
        R1.1 & G1 & UC2    & SD2  \\
        R1.2 & G1 & UC3    & SD3  \\
        R1.3 & G1 & UC6    & SD6  \\
        \bottomrule
        \end{tabularx}
        \caption{Requirements Mapping}
        \label{tab:requirements}
    \end{table}

    \begin{longtable}{|p{0.50\textwidth}|p{0.50\textwidth}|}
        \hline
        \textbf{Term} & \textbf{Description} \\
        \hline
        \endfirsthead
        \hline
        \textbf{Term} & \textbf{Description} \\
        \hline
        \endhead
        \hline
        \endfoot
        
        Internship, Placement, Work-Experience & A temporary work opportunity offered by a company, designed for students to gain practical experience in a professional environment while applying their academic knowledge. \\
        \hline
        CV, Resume & A document created by a student containing their personal information, skills, educational background, and work experience, used to apply for internships or jobs. \\
        \hline
        Recommendation System, Suggestion System & A feature of the platform that identifies and matches suitable internships for students or suitable candidates for companies based on their profiles, preferences, and requirements. \\
        \hline
        Student Profile, User Profile & A digital representation of a student within the system, containing personal details, uploaded CVs, skills, and internship applications. \\
        \hline
        Company Profile & A digital representation of a company within the system, containing details about the company, uploaded projects or internships, and any associated preferences or requirements. \\
        \hline
        Matching Process, Recommendation Process & The sequence of steps executed by the system to align the skills and preferences of students with the requirements of available internships offered by companies. \\
        \hline
        Feedback, Review & Information collected from students and companies after the internship or during the process to refine the matching system and improve user satisfaction. \\
        \hline
        Communication Space, Chat Feature, Messaging System & A feature in the platform that allows students, companies, and universities to interact and share important updates or resolve concerns. \\
        \hline
        Selection Process & A phase in which companies evaluate student applications, conduct interviews, and finalize the selection of candidates for internships. \\
        \hline
        Interview Setup, Interview Management & The process supported by the system to schedule, conduct, and manage interviews between companies and students. \\
        \hline
        Contract Signing & A formal agreement between a student and a company, signifying the acceptance of terms for an internship. \\
        \hline
        University Monitoring & The process where the university oversees the activities and outcomes of student internships and intervenes if necessary. \\
        \hline
        Complaint Resolution & The process of identifying and addressing issues raised by students or companies during or after the internship period. \\
        \hline
        Submission Deadline, Application Deadline & The last date for students to submit applications for an internship or for companies to post available projects on the platform. \\
        \hline
        Notification System, Alert System & A functionality in the platform that keeps users informed about new opportunities, deadlines, or important events. \\
        \hline
        Platform, System, Application & All synonyms for the software platform being developed to manage the interactions and processes related to internships. \\
        \hline
        Mentorship, Guidance & Support provided by a company representative to a student during their internship to ensure they achieve both learning objectives and project goals. \\
        \hline
        Statistical Analysis, Data Insights & The process by which the system evaluates collected feedback and interactions to improve its recommendation algorithms and user experience. \\
        \hline
        
    \end{longtable}
        